Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-10-11 manuscript/manuscript.tex
minor changes for final MEE files

We compared the forecasting skill
\textcolor{blue}{(accuracy and precision)} of statistical and population
models based on aggregated, population-level data with the skill of
models based on individual-level data. We used a demographic dataset
that tracks the fates of individual plants from four species over 14
years to build two kinds of single-species population models,
traditional models using individual growth, survival, and recruitment
data and alternative models based on population-level (basal cover)
data. We simulated from the models to answer two questions motivated by
the fact that the effects of intraspecific competition (density
dependence) and interannual weather variability act at the level of the
individual (Clark et al. 2011). First, can population models fit using
aggregated individual-level data (percent cover) adequately capture
density dependence to produce forecasts as skillful as those from models
fit to demographic data? Second, can population models fit using
aggregated data adequately capture the influence of climate on
population growth and, in turn, produce forecasts as skillful as those
from models fit to demographic data?

@@

\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations. Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
For both model types (IPM and QBM), we fit and simulate versions of the model with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data. We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon}
(Petchey et al. 2015).

@@

This cross-validation procedure allowed us to compare the accuracy and
precision of the two modeling approaches (IPM versus QBM) with and
without climate covariates. We first calculated the median predicted
cover across the 100 simulations for each quadrat-year and then
calculated forecast skill as the correlation (\(\rho\)) between
forecasts and observations. We calculated forecast error as mean
absolute error (MAE) between forecasts and observations. We compared
\(\rho\) and MAE between model types and within model types between
models with and without climate covariates using one-sided \emph{t}
tests with adjusted degrees of freedom following Wilcox (2009) and
standard errors calculated using the HC4 estimator of Cribari-Neto
(2004). Statistical tests
\textcolor{blue}{for comparing correlations and error} were conducted
using algorithms from Ye et al. (2015).

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon}
(Petchey et al. 2015). To assess the forecast horizons of our models, we
initiate the forecast model with the population state at some time
\emph{t} and make sequential forecasts of the population at times
\(t+1, t+2, \dots, t+T\) where \emph{T} is the maximum number of years
between the initial year and the final year of our observations. For
example, if we initialize the forecast model with percent cover in 1940,
we are able to make five forecasts up to the year 1945. Forecast models
are not re-initialized with observations between years. Thus, in our
current example, the model forecast for percent cover in 1941 has a
forecast horizon of one year, the forecast in 1942 has a forecast
horizon of two years, and so on. We performed these simulations using
mean parameter values for all model types (IPM with/without climate; QBM
with/without climate) and all possible initial years. For a given
forecast distance, we averaged the correlation between forecasts and
observations. Note that our forecasts for the horizon analysis are all
made using in-sample data because we used model fits from the full data
set. Nonetheless, our simulations offer insight into the differences
among model forecast horizons.
\textcolor{blue}{We chose an arbitrary forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold. the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.
For basic research on forecasting, arbitrary proficiency thresholds suffice for comparative purposes}
(Petchey et al. 2015),
\textcolor{blue}{and $\rho = 0.5$ represents the point at which about 25\% of the variance in observations is explained by the predictions.}

@@

With climate covariates included
\textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased},
but they did so at similar rates (Fig. 4). The only exception is for
\emph{Poa secunda}, where QBM forecast accuracy remained steady as the
\textcolor{blue}{temporal distance of the forecast increased}, whereas
IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (\emph{P} > 0.05 for all one-sided \emph{t}-tests, Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast proficiency threshold by a large margin (Fig. 4, Table S24).}

@@

We also expected the inclusion of environmental forcing to reveal
further differences between the models. Interannual variation in weather
can affect vital rates in different ways (Dalgleish et al. 2011). Thus,
estimates of climate effects on plant population growth may be biased or
non-identifiable when the underlying statistical model is fit using
population-level data that integrates over the potentially unique
climate responses of individual vital rates. We found some evidence that
the QBM failed to detect climate effects for three species (\emph{B.
gracilis}, \emph{H. comata}, and \emph{Poa secunda}), where important
climate effects were identified in the individual vital rate models but
not in the percent cover model (Fig. 3).
\textcolor{blue}{For \emph{H. comata}, adding climate covariates did not improve forecasts (Fig. 2), despite the significant climate effects in the vital rate regressions (Fig. 3).}
Furthermore, for the two species where including climate covariates
increased forecast accuracy (\emph{B. gracilis} and \emph{Poa secunda}),
forecast accuracy (Fig. 2) and error (Fig. S2) were equivalent between
the IPM and QBM.

@@

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the
\textcolor{blue}{time between the model initialization and the forecast increased.}
In principle, more mechanistic models should produce better predictions,
especially under novel conditions (Evans 2012, Schindler and Hilborn
2015). In our case, the IPM explicitly models the influence of weather
on recruitment and survival, effects that may be poorly represented in
the QBM because recruitment and survival mainly affect small plants that
contribute little to year-to-year changes in percent cover. Over longer
time scales, the addition and subtraction of small plants could have
large effects on population growth, so explicitly modeling these effects
could contribute to a longer forecast horizon. However, we found no
evidence
\textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes and parameters, which can reduce bias due to parameter uncertainty.
As a result, the QBM may better capture near term dynamics when populations do not fluctuate widely, as in our case.}

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling methods (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters}
(Queenborough et al. 2011).
\textcolor{blue}{Percent cover models based on data containing more measurement error than ours might perform worse in comparison with individual-based models.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)}
(Hobbs and Hooten 2015).

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have few ideas about how to improve population forecasts that have not already been proposed}
(Mouquet et al. 2015, Petchey et al. 2015).
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate}
(Teller et al. 2016),
\textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty}
(Petchey et al. 2015).
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts}
(Petchey et al. 2015).
\textcolor{blue}{Whether the poor predictive ability of our models impacts the comparison of models based on individual vs. population-level data is an open question}.

@@

The data used in this paper have been archived on Ecological Archives:
\url{http://esapubs.org/archive/ecol/E092/143/}. All data and R code
necessary to reproduce our work has been deposited on
\textcolor{blue}{Figshare} (link) and is also available on GitHub
(\url{http://github.com/atredennick/MicroMesoForecast}).

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=6in]{./components/forecast_accuracy_mockup_boxplot.png}
  \caption{Comparisons of one-step-ahead, out-of-sample forecast accuracy between the IPM and QBM models with and without the inclusion of climate covariates. \textcolor{blue}{Boxplots show the distribution of $\rho$ averaged over quadrats for each cross-validation year (i.e., 13 values of $\rho$ for each species-model combination).} For each comparison, \emph{P}-values are from one-sided \emph{t} tests designed to assess whether the first model in the comparison statement had higher accuracy than the second model in the comparison statement (see details in Table S22). \textcolor{blue}{Statistical tests relied on correlation values for each quadrat-year-species combination, after averaging over model reps for each combination.} In no case did adding climate covariates decrease forecast accuracy (Table S21). Species codes are as in Fig. 1.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=7in]{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Because our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients). Kernel bandwidths of posterior densities were adjusted by a factor of 4 for visual clarity. Species codes are as in Fig. 1. \textcolor{blue}{Climate covariate codes: \emph{pptLag} = "water year" precipitation at \emph{t}-2; \emph{ppt1} = April through June precipitation at \emph{t}-1; \emph{ppt2} = April through June precipitation at \emph{t}; \emph{TmeanSpr1} = April through June temperature at \emph{t}-1; \emph{TmeanSpr2} = April through June temperature at \emph{t}.}}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{./components/forecast_horizon.png}
  \caption{The forecast horizons for both models with climate covariates included \textcolor{blue}{and using mean parameter values. Points show the average accuracy ($\rho$, \textcolor{blue}{correlation between observations and predictions}) across all forecasts at a given distance between the last observation and the forecast, where forecasts are made for in-sample data.} We only examine the forecast accuracy of models with climate covariates included because in no case did including climate covariates significantly decrease accuracy (see Fig. 2). \textcolor{blue}{The dashed blue line indicates a forecast proficiency threshold of $\rho = 0.5$. Species codes are as in Fig. 1 and statistical comparisons between the IPM and QBM at each forecast distance are in Tables S23 and S24.}}
\end{figure}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

@@

>>>>

We compared the forecasting skill (accuracy and precision) of
statistical and population models based on aggregated, population-level
data with the skill of models based on individual-level data. We used a
demographic dataset that tracks the fates of individual plants from four
species over 14 years to build two kinds of single-species population
models, traditional models using individual growth, survival, and
recruitment data and alternative models based on population-level (basal
cover) data. We simulated from the models to answer two questions
motivated by the fact that the effects of intraspecific competition
(density dependence) and interannual weather variability act at the
level of the individual (Clark et al. 2011). First, can population
models fit using aggregated individual-level data (percent cover)
adequately capture density dependence to produce forecasts as skillful
as those from models fit to demographic data? Second, can population
models fit using aggregated data adequately capture the influence of
climate on population growth and, in turn, produce forecasts as skillful
as those from models fit to demographic data?

@@

We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions
(survival, growth, and rectruitment) to build an Integral Projection
Model (IPM) for simulating the plant populations. Using the percent
cover data we fit a simple, Gompertz population growth model, which we
refer to as a quadrat-based model (QBM). For both model types (IPM and
QBM), we fit and simulate versions of the model with and without climate
covariates. We used Bayesian ridge regression to weight the importance
of each climate covariate. We then performed cross-validation to assess
each model's ability to predict out-of-sample data. We compared the
forecast accuracy (\(\rho\), correlation between observations and
predictions) and mean absolute error (MAE) between the IPM and the QBM
to test our expectation that the IPM should outperform the QBM. Lastly,
we use in-sample forecasts to quantify each model's forecast horizon
(Petchey et al. 2015).

@@

This cross-validation procedure allowed us to compare the accuracy and
precision of the two modeling approaches (IPM versus QBM) with and
without climate covariates. We first calculated the median predicted
cover across the 100 simulations for each quadrat-year and then
calculated forecast skill as the correlation (\(\rho\)) between
forecasts and observations. We calculated forecast error as mean
absolute error (MAE) between forecasts and observations. We compared
\(\rho\) and MAE between model types and within model types between
models with and without climate covariates using one-sided \emph{t}
tests with adjusted degrees of freedom following Wilcox (2009) and
standard errors calculated using the HC4 estimator of Cribari-Neto
(2004). Statistical tests for comparing correlations and error were
conducted using algorithms from Ye et al. (2015).

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases. In particular, we are interested in the temporal
distance at which forecast skill falls below a threshold: the so-called
ecological forecast horizon (Petchey et al. 2015). To assess the
forecast horizons of our models, we initiate the forecast model with the
population state at some time \emph{t} and make sequential forecasts of
the population at times \(t+1, t+2, \dots, t+T\) where \emph{T} is the
maximum number of years between the initial year and the final year of
our observations. For example, if we initialize the forecast model with
percent cover in 1940, we are able to make five forecasts up to the year
1945. Forecast models are not re-initialized with observations between
years. Thus, in our current example, the model forecast for percent
cover in 1941 has a forecast horizon of one year, the forecast in 1942
has a forecast horizon of two years, and so on. We performed these
simulations using mean parameter values for all model types (IPM
with/without climate; QBM with/without climate) and all possible initial
years. For a given forecast distance, we averaged the correlation
between forecasts and observations. Note that our forecasts for the
horizon analysis are all made using in-sample data because we used model
fits from the full data set. Nonetheless, our simulations offer insight
into the differences among model forecast horizons. We chose an
arbitrary forecast accuracy of \(\rho = 0.5\) as our forecast
proficiency threshold. the forecast horizon is the temporal distance at
which forecast accuracy falls below \(\rho = 0.5\). For basic research
on forecasting, arbitrary proficiency thresholds suffice for comparative
purposes (Petchey et al. 2015), and \(\rho = 0.5\) represents the point
at which about 25\% of the variance in observations is explained by the
predictions.

@@

With climate covariates included and using mean parameter values, the
accuracy of both models' forecasts declined as the distance between the
last observation and the forecast increased, but they did so at similar
rates (Fig. 4). The only exception is for \emph{Poa secunda}, where QBM
forecast accuracy remained steady as the temporal distance of the
forecast increased, whereas IPM forecast accuracy declined (Fig. 4). The
forecast horizons were short: forecast accuracy fell below \(\rho\) =
0.5 after one year for the IPM for most species, and after four years,
at most, for the QBM (Fig. 4). Across the different temporal distances
from the observation to the forecast, the IPM was never more accurate
than the QBM (\emph{P} \textgreater{} 0.05 for all one-sided
\emph{t}-tests, Table S23). Likewise, the QBM was rarely more accurate
the IPM, the only exception being for \emph{H. comata} at temporal
distances of two (\(t_{(115)}\) = 2.39, \emph{P} = 0.002) and three
years (\(t_{(98)}\) = 2.04, \emph{P} = 0.022) (Table S24). There were
some cases where the QBM was more accurate than the IPM for
\emph{Poa secunda}, but neither model exceeded the forecast proficiency
threshold by a large margin (Fig. 4, Table S24).

@@

We also expected the inclusion of environmental forcing to reveal
further differences between the models. Interannual variation in weather
can affect vital rates in different ways (Dalgleish et al. 2011). Thus,
estimates of climate effects on plant population growth may be biased or
non-identifiable when the underlying statistical model is fit using
population-level data that integrates over the potentially unique
climate responses of individual vital rates. We found some evidence that
the QBM failed to detect climate effects for three species (\emph{B.
gracilis}, \emph{H. comata}, and \emph{Poa secunda}), where important
climate effects were identified in the individual vital rate models but
not in the percent cover model (Fig. 3). For \emph{H. comata}, adding
climate covariates did not improve forecasts (Fig. 2), despite the
significant climate effects in the vital rate regressions (Fig. 3).
Furthermore, for the two species where including climate covariates
increased forecast accuracy (\emph{B. gracilis} and \emph{Poa secunda}),
forecast accuracy (Fig. 2) and error (Fig. S2) were equivalent between
the IPM and QBM.

@@

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the time between the model initialization and the forecast
increased. In principle, more mechanistic models should produce better
predictions, especially under novel conditions (Evans 2012, Schindler
and Hilborn 2015). In our case, the IPM explicitly models the influence
of weather on recruitment and survival, effects that may be poorly
represented in the QBM because recruitment and survival mainly affect
small plants that contribute little to year-to-year changes in percent
cover. Over longer time scales, the addition and subtraction of small
plants could have large effects on population growth, so explicitly
modeling these effects could contribute to a longer forecast horizon.
However, we found no evidence that the forecast horizon for the IPM was
greater than the QBM (Fig. 4). On the contrary, the QBM tended to have a
slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes and parameters, which can reduce bias due to
parameter uncertainty. As a result, the QBM may better capture near term
dynamics when populations do not fluctuate widely, as in our case.

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach. Third, our percent cover data are essentially
error-free because we were able to aggregate indiviual plant areas to
calculate percent cover. Percent cover data collected by typical
sampling methods (e.g., Daubenmire frames) will include error that may
affect population forecasts due to misspecifing the initial conditions
and/or biasing model parameters (Queenborough et al. 2011). Percent
cover models based on data containing more measurement error than ours
might perform worse in comparison with individual-based models. One way
to account for such error is to develop a sampling model that relates
the observations (estimated percent cover in a plot) to the true state
(percent cover derived from individual plant measurements in the same
plot) (Hobbs and Hooten 2015).

Although our main goal was to compare individual-based and
population-level modeling approaches relative to one another, it is
worth reflecting on the absolute forecasting skill of our models. In
particular, the forecast horizon of both models, defined as the time
horizon at which the correlation between predictions and observations
falls below \(\rho = 0.5\), is less than five years for all species.
Such short forecast horizons are not encouraging. Unfortunately, we have
few ideas about how to improve population forecasts that have not
already been proposed (Mouquet et al. 2015, Petchey et al. 2015). Longer
time-series should improve our ability to detect exogenous drivers such
as climate (Teller et al. 2016), and modeling larger spatial extents may
reduce parameter uncertainty (Petchey et al. 2015). We may also have to
shift our perspective from making explicit point forecasts to making
moving average forecasts (Petchey et al. 2015). Whether the poor
predictive ability of our models impacts the comparison of models based
on individual vs.~population-level data is an open question.

@@

The data used in this paper have been archived on Ecological Archives:
\url{http://esapubs.org/archive/ecol/E092/143/}. All data and R code
necessary to reproduce our work has been deposited on Figshare
(\url{http://doi.org/10.6084/m9.figshare.4007520}) and is also available
on GitHub
(\url{http://github.com/atredennick/MicroMesoForecast/releases/tag/v1.0}).

\subsection{Author Contributions}\label{author-contributions}

ATT and PBA conceived the study; ATT, MBH, and PBA developed the
statistical and modeling approach; ATT did the data analysis, with input
from MBH and PBA; ATT wrote the first draft of the manuscript and all
authors contributed to revisions.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=6in]{./components/forecast_accuracy_mockup_boxplot.png}
  \caption{Comparisons of one-step-ahead, out-of-sample forecast accuracy between the IPM and QBM models with and without the inclusion of climate covariates. Boxplots show the distribution of $\rho$ averaged over quadrats for each cross-validation year (i.e., 13 values of $\rho$ for each species-model combination). For each comparison, \emph{P}-values are from one-sided \emph{t} tests designed to assess whether the first model in the comparison statement had higher accuracy than the second model in the comparison statement (see details in Table S22). Statistical tests relied on correlation values for each quadrat-year-species combination, after averaging over model reps for each combination. In no case did adding climate covariates decrease forecast accuracy (Table S21). Species codes are as in Fig. 1.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=7in]{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Because our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients). Kernel bandwidths of posterior densities were adjusted by a factor of 4 for visual clarity. Species codes are as in Fig. 1. Climate covariate codes: \emph{pptLag} = "water year" precipitation at \emph{t}-2; \emph{ppt1} = April through June precipitation at \emph{t}-1; \emph{ppt2} = April through June precipitation at \emph{t}; \emph{TmeanSpr1} = April through June temperature at \emph{t}-1; \emph{TmeanSpr2} = April through June temperature at \emph{t}.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{./components/forecast_horizon.png}
  \caption{The forecast horizons for both models with climate covariates included and using mean parameter values. Points show the average accuracy ($\rho$,correlation between observations and predictions) across all forecasts at a given distance between the last observation and the forecast, where forecasts are made for in-sample data. We only examine the forecast accuracy of models with climate covariates included because in no case did including climate covariates significantly decrease accuracy (see Fig. 2). The dashed blue line indicates a forecast proficiency threshold of $\rho = 0.5$. Species codes are as in Fig. 1 and statistical comparisons between the IPM and QBM at each forecast distance are in Tables S23 and S24.}
\end{figure}

@@

\subsection{References}\label{references}
\addcontentsline{toc}{subsection}{References}

@@

\subsection{Supporting Information}\label{si}
\begin{description}
  \item[Appendix S1.] Detailed methods and Stan code examples for the vital rate and percent cover regressions; Figures S1 and S2; Tables S1-S24.
\end{description
